Automating Verification of MPC Security

### 2023-06-11 popl24/bruteforce.tex
checkpoint

\subsection{Method 1: Enumerating $\runs(\prog)$}

@@

In order to automatically obtain $\runs(\prog)$, we can do a left
folding of $\solve$ across $\prog$, inductively extending memories
with valid view assignments in the order of their definition.
We can then use this to compute $\progd(\prog)$. We denote
these computations as $\cruns$ and $\progd$ respectively.
\begin{lemma}
  \label{lemma-cruns}
  Given $\prog$ where $\iov(\prog) = S \cup V$ and $\flips(\prog) = F$. Define:
  \begin{eqnarray*}
    {tt}\ \ \stores\ (\eassign{\view{\cid}{w}}{\be}) &\defeq& \begin{array}{l}
      \mathrm{let}\ \stores' = \solve{\stores}{\be} \ \mathrm{in}\\
      \ \ \{\extend{\store}{\view{\cid}{w}}{1} \mid \store \in \stores' \}\ \cup\\
      \ \ \{\extend{\store}{\view{\cid}{w}}{0} \mid \store \in \stores - \stores' \}\end{array}\\[2mm]
    \cruns(\prog) &\defeq& \mathit{foldl}\ {tt}\ \mems(S \cup F)\ \prog
  \end{eqnarray*}
  Then $\cruns(\prog) = \runs(\prog)$.
\end{lemma}
\begin{proof}
  By Lemma \ref{lemma-solves} and induction on the length of $\prog$. 
\end{proof}
\begin{lemma}
  \label{lemma-cprogd}
  Given $\prog$ where $\iov(\prog) = S \cup V$ and $\flips(\prog) = F$. Define
  $\cprogd(\prog)$ as the distribution $\margd{\pdf{S \cup F \cup V}}{S\cup V}$,
  where:
  $$
  \pdf{S \cup F \cup V}(\store) = \begin{cases}1/2^{|S \cup F|} & \text{if\ } \store \in
    \cruns(\prog) \\ 0 & \text{otherwise} \end{cases} 
  $$
  Then:
  $$
  \cprogd(\prog) = \progd(\prog)
  $$
\end{lemma}
\begin{proof}
  Immediately by Lemma \ref{lemma-cruns} and Definition \ref{def-progd}.
\end{proof}

@@

\subsection{Method 2: Rewriting to Datalog}
\label{section-bruteforce-datalog}

Here we show how to rewrite any $\prog$ to an equivalent Datalog
program, which supports application of recent work in linear algebraic
interpretation of Datalog and optimizations of model computation on
high performance computers \cite{XXX}. The method here also enumerates
$\runs(\prog)$ memory-by-memory, rather than in a ``batched'' manner
as in our first method, allowing parallelization of model
computation. The rewriting we describe here is to Datalog with
negation, with a negation-as-failure model. Here is the syntax,
where \emph{atoms} are $\minicat$ variables, \emph{literals}
are atoms or negated atoms, and clause bodies are conjunctions of literals.
A \emph{Datalog program} is a list of clauses.
$$
\begin{array}{rclr}
  \alpha &::=& \view{\cid}{w} \mid  \secret{\cid}{w} \mid \flip{\cid}{w} \mid \oracle{w} & \qquad \textit{(atoms)}\\
  \mathit{body} &::=&  \alpha \mid \neg \alpha \mid alpha \wedge \mathit{body} \mid \neg\alpha \wedge \mathit{body} \mid \varnothing \\
  \mathit{clause} &::=& \alpha \gets \mathit{body}
\end{array}
$$
We can use techniques in \cite{XXX} to also eliminate negation from
resulting programs, this presentation is just to summarize our
fundamental approach.

>>>>

\subsection{Method 1: Inductive Computation of $\runs(\prog)$}

@@

In order to automatically obtain $\runs(\prog)$, we can do a left
folding of $\solve$ across $\prog$, inductively extending memories
with valid view assignments in the order of their definition.
We can then use this to compute $\progd(\prog)$. We denote
these computations as $\cruns$ and $\cprogd$ respectively.
\begin{lemma}
  \label{lemma-cruns}
  Given $\prog$ where $\iov(\prog) = S \cup V$ and $\flips(\prog) = F$. Define:
  \begin{eqnarray*}
    {tt}\ \ \stores\ (\eassign{\view{\cid}{w}}{\be}) &\defeq& \begin{array}{l}
      \mathrm{let}\ \stores' = \solve{\stores}{\be} \ \mathrm{in}\\
      \ \ \{\extend{\store}{\view{\cid}{w}}{1} \mid \store \in \stores' \}\ \cup\\
      \ \ \{\extend{\store}{\view{\cid}{w}}{0} \mid \store \in \stores - \stores' \}\end{array}\\[2mm]
    \cruns(\prog) &\defeq& \mathit{foldl}\ {tt}\ \mems(S \cup F)\ \prog
  \end{eqnarray*}
  Then $\cruns(\prog) = \runs(\prog)$.
\end{lemma}
\begin{proof}
  By Lemma \ref{lemma-solves} and induction on the length of $\prog$. 
\end{proof}
\begin{lemma}
  \label{lemma-cprogd}
  Given $\prog$ where $\iov(\prog) = S \cup V$ and $\flips(\prog) = F$. Define
  $\cprogd(\prog)$ as the distribution $\margd{\pdf{S \cup F \cup V}}{S\cup V}$,
  where:
  $$
  \pdf{S \cup F \cup V}(\store) = \begin{cases}1/2^{|S \cup F|} & \text{if\ } \store \in
    \cruns(\prog) \\ 0 & \text{otherwise} \end{cases} 
  $$
  Then:
  $$
  \cprogd(\prog) = \progd(\prog)
  $$
\end{lemma}
\begin{proof}
  Immediately by Lemma \ref{lemma-cruns} and Definition \ref{def-progd}.
\end{proof}

@@

\subsection{Method 2: Conversion to Datalog}
\label{section-bruteforce-datalog}

Here we show how to rewrite any $\prog$ to an equivalent Datalog
program, which supports application of recent work in linear algebraic
interpretation of Datalog and optimizations of model computation on
high performance computers \cite{XXX}. The method here also enumerates
$\runs(\prog)$ memory-by-memory, rather than in a ``batched'' manner
as in our first method, allowing parallelization of model
computation. The rewriting we describe here is to Datalog with
negation, with a negation-as-failure model, though we can use also
use techniques in \cite{XXX} to also eliminate negation from
resulting programs. \emph{Atoms} are $\minicat$ variables, \emph{literals}
are atoms or negated atoms, and clause bodies are conjunctions of literals.
A \emph{Datalog program} is a list of clauses.
$$
\begin{array}{rclr}
  \alpha &::=& \view{\cid}{w} \mid  \secret{\cid}{w} \mid \flip{\cid}{w} \mid \oracle{w} & \qquad \textit{(atoms)}\\
  \mathit{body} &::=&  \alpha \mid \neg \alpha \mid \alpha \wedge \mathit{body} \mid \neg\alpha \wedge \mathit{body} \mid \varnothing \\
  \mathit{clause} &::=& \alpha \gets \mathit{body}
\end{array}
$$

### 2023-06-11 popl24/hyperprop.tex
checkpoint

The simulator is given just the corrupt inputs to the run- that is,
$\store_{S_C}$- and the output of the protocol- that is,
$\idealf(\store)$- and aims to reconstruct the distribution of
adversarial views observed in the real world. The intuition here is
that the simulator is given the information that is necessarily
available to the adversary by observing a run of the protocl, and if
the simulator can reconstruct whatever information appears in the real
world adversarial views, by reconstructing their distributions, then
those views leak no additional information, i.e., they have no
additional dependencies on honest input secrets than what is revealed
by the output and conditionings on corrupt inputs.

>>>>

The simulator is given just the corrupt inputs to the run- that is,
$\store_{S_C}$- and the output of the protocol- that is,
$\idealf(\store)$- and aims to reconstruct the distribution of
adversarial views observed in the real world. The intuition here is
that the simulator is given the information that is necessarily
available to the adversary by observing a run of the protocol, and if
the simulator can reconstruct whatever information appears in the real
world adversarial views, by reconstructing their distributions, then
those views leak no additional information, i.e., they have no
additional dependencies on honest input secrets than what is revealed
by the output and conditionings on corrupt inputs.
